Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-05-22 docs/thesis/cover.tex
thesis minor edits

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Youssef M. Marzouk}{Chairman, Department Committee on Graduate Theses}

@@

The success I achieved in completing this thesis was only possible because of the incredible support from family, friends, mentors, and MIT faculty.
I was able to complete this thesis a full year ealier than I expected and I must thank the many people who made that possible.

I first need to thank my family beginning with my beautiful wife, Jasmine.  
Her support and encouragement have been unwavering.  
When I was up late struggling with a problem, she never believed I wouldn't figure it out.  
She has always been enthusiastic and supportive of my successes and given sound advice and encouragment when facing difficult problems or situations. 
I could not have done this without her.

My parents and sibilings were also constant sources of support and encouragement. 
My parents are the wisest people I know and I am immensely grateful for their advice.  
They have always pushed me to be the best me and I would not have ever made it to MIT without them.

I want to greatly thank my advisor, Warren Hoburg (Woody), for his guidance, friendship, and belief in my abilities.  
Woody is a demanding advisor, who pushed me to learn, grow, and develop at a pace and intensity that would not have been possible otherwise. 
While rigorous in his pursuit of high quality work, Woody also gave me the flexibility to explore my own interests and taught me to think critically for myself.
He is truly a brillant professor and I was fortunate that he selected me to join his lab this year.

I would not have made it through the rigors and stress of MIT without my best friend and officemate Martin York. 
I could not have shared an office with a more brillant, passionate and fun person. 
Our common interests, beliefs, and mentality gave me freedom to express my views, opinions, challenges and successes without fear of judgement or offense.

I also need to thank the project managers, professors, and sponsors of the Jungle Hawk Owl, John Hansmen, Navid Yazdani, Mark Drela, Warren Hoburg and Tony Tao. 
The original problem developed by this team of professionals, of which architecture would was best for the Jungle Hawk Owl was the basis for my thesis work.
They all acted as mentors to me, teaching me techincally, guiding me in the industry and giving me opportunites to present my work. 
It was a privilege to work with and for these people to build the Jungle Hawk Owl.

Finally, I want to thank the many fellow students I worked with over the past year and a half building and designing the Jungle Hawk Owl.  
We went through an extremely intense and rapid design and build cycle. 
The late nights, long, arduous layups, and successful test flights have forged a camaraderie between us that I will not forget.

>>>>

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Youssef M. Marzouk}{Associate Professor of Aeronautics and Astonautics\\Chairman, Graduate Program Committee}

@@

\begin{singlespace}
The success I achieved in completing this thesis a year earlier than expected was only possible because of the incredible support from family, friends, mentors, and MIT faculty.

I first need to thank my family, beginning with my beautiful wife, Jasmine.  
Her support and encouragement have been unwavering.  
When I was up late struggling with a problem, she always believed I would figure it out.  
She has been enthusiastic and supportive of my successes and given sound advice and encouragement when facing difficult problems or situations. 
I could not have done this without her.

My parents and siblings were also constant sources of support and encouragement. 
My parents are the wisest people I know and I am immensely grateful for their advice.  
They have pushed me to be the best me and I would not have ever made it to MIT without them.

I want to thank my outstanding advisor, Warren Hoburg (Woody), for his guidance, friendship, and belief in my abilities.  
Woody is a demanding advisor who pushed me to learn, grow, and develop at a pace and intensity that I did not believe possible. 
While rigorous in his pursuit of high quality work, Woody also gave me the flexibility to explore my own interests and taught me to think critically for myself.
He is truly a brilliant professor and a wise mentor and I was fortunate that he selected me to join his lab this year.

I would not have made it through the rigors and stress of MIT without my best friend and officemate Martin York. 
I could not have shared an office with a more brilliant, passionate and fun person. 
Our common interests, beliefs, and convictions gave me freedom to express my views, opinions, challenges and successes without fear of judgement or offense.

I also need to thank the project managers, professors, and sponsors of the Jungle Hawk Owl, John Hansmen, Navid Yazdani, Mark Drela, Warren Hoburg and Tony Tao. 
The original problem developed by this team of professionals, of which architecture would was best for the Jungle Hawk Owl was the basis for my thesis work.
They all acted as mentors to me, teaching me technically, guiding me in the industry and giving me opportunities to present my work. 
It was a privilege to work with and for these people to build the Jungle Hawk Owl.

Finally, I want to thank the many fellow students I worked with over the past year and a half building and designing the Jungle Hawk Owl.  
We went through an extremely intense and rapid design and build cycle. 
The late nights, long, arduous layups, and successful test flights have forged a camaraderie between us that I will not forget. 
\end{singlespace}
